Hypercoercions and a Framework for \\ Equivalence of Cast Calculi

### 2020-01-04 paper.tex
add corollary: reformulated weak bisim S(C) D

>>>>

\begin{corollary}[Weak Bisimulation between \effCEK{C} and \ineffCEKD{}, 
reformulated]
  Assume $C$ implements Lazy D Cast ADT
  and $C$ is a monoid
  and $cast(T,l,T)=id(T)$,
  $s_1 \approx s_1'$,
\begin{enumerate}
	\item If $\judgeSreduce{C}{s_1}{s}$ for some $s$, then
	$\judgeSreduceTrans{C}{s}{s_2}$, and
	$\judgeDreducePlus{s_1'}{s_2'}$,
	$s_2 \approx s_2'$ for some $s_2$ and $s_2'$.
	\item If $\judgeDreduce{s_1'}{s'}$ for some $s'$, then
	$\judgeDreduceTrans{s'}{s_2'}$, and
	$\judgeSreducePlus{C}{s_1}{s_2}$,
	$s_2 \approx s_2'$ for some $s_2$ and $s_2'$.
	\item $s_1 = \sOOhalt{o}$ if and only if  $s_1' = \sOOhalt{o}$
\end{enumerate}
\end{corollary}
\begin{proof}
	By applying Lemma~\ref{lem:weak-bisim-SC-D} on $s_1 \approx s_1'$ and case 
	analysis.
\end{proof}
